Parameter-less Population Pyramid

### 2014-03-31 Parameterless Population Pyramid/main.tex
Fixed copywrite notice, take 2.

\permission{Permission to make digital or hard copies of part or all of this work
for personal or classroom use is granted without fee provided that copies are not
made or distributed for profit or commercial advantage, and that copies bear this
notice and the full citation on the first page. Copyrights for third-party
components of this work must be honored. For all other uses, contact the
owner/author(s). Copyright is held by the author/owner(s).}
\conferenceinfo{GECCO'14,}{July 12--16, 2014, Vancouver, BC, Canada.}
\copyrightetc{ACM \the\acmcopyr}
\crdata{978-1-4503-1964-5/14/07. \\ http://dx.doi.org/10.1145/2576768.2598350}

>>>>

\permission{Permission to make digital or hard copies of all or part of this work
for personal or classroom use is granted without fee provided that copies are not
made or distributed for profit or commercial advantage and that copies bear this
notice and the full citation on the first page. Copyrights for components of this
work owned by others than ACM must be honored. Abstracting with credit is permitted.
To copy otherwise, or republish, to post on servers or to redistribute to lists,
requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
\conferenceinfo{GECCO'14,}{July 12--16, 2014, Vancouver, BC, Canada.}
\copyrightetc{Copyright 2014 ACM \the\acmcopyr}
\crdata{978-1-4503-2662-9/14/07\ ...\$15.00. \\ http://dx.doi.org/10.1145/2576768.2598350}
